Le titre

### 2022-09-07 Manuscrit Thèse/chapter 1/Chapter 1.tex
nuno

Ccl sur le fait que osef pour les échantillon en excès de N mais que ça peut avoir de l'importance avec les samples low en impurities.

>>>>

For samples in high excess of [N$_s$] such as type Ib HPHT diamonds, the question of the charge state of the NV center is of relatively low importance as the NV$^-$ state is the predominant one. For sample with a lower [N$_s$] content and a higher [NV]/[N$_s$] ratio however, one must be more careful with the optical intensity and wavelength used as the concentration of [NV$^0$] can reach 50\% of the total [NV] concentration and even more [les refs chez achard et barry]

\section{The NV$^-$ center physics}
